---
title: "Replication of Fama and French (2010, JF)"
output: html_notebook
---


```{r setup, include = FALSE}
library(MatchIt)
library(plyr)
library(dplyr)
library(tidyverse)
library(lubridate)
library(zoo)
library(broom)
library(timereg)
library(plm)
library(lfe)
library(aTSA)
library(foreign)
library(readr)
library(lmtest)
library(sandwich)
library(readstata13)
library(fixest)
library(fastDummies)
library(ivmodel)
library(panelr)
library(latticeExtra)
library(reshape2)

```

```{r}
setwd('/Users/yanpingzhu/Desktop/Courses/BUSI 525 Topics in Financial Markets Research/Replication')
```

# Replication of Table 2

## Load fund summary and return data, and fama french factors
```{r}
#fund summary data (yearly)
fund_summ <- read.csv("./Data/fund_summ.csv", header = TRUE)

df_fund_summ <- fund_summ %>% 
  #create date variable
  mutate(caldt          = as.Date(as.character(caldt), format="%Y%m%d"),
         year           = year(caldt)) %>% 
        # first_offer_dt = as.Date(as.character(first_offer_dt), format = "%Y%m%d")) %>% 
  #include only funds that invest in US common stocks (obj_cd = ED)
  mutate(obj_cd  = str_sub(crsp_obj_cd, 1,2)) %>% 
  filter(obj_cd  == "ED") %>% 
  #exclude index funds
  filter(index_fund_flag == "") %>% 
  select(crsp_fundno, fund_name, year, exp_ratio) 


#fund return and ff factors data (monthly)
ret_ff <- read.csv("./Data/ret_ff.csv", header = TRUE)

df_fund_ret <- ret_ff %>% 
  mutate(#create date variables
         caldt          = as.Date(as.character(caldt), format="%Y%m%d"),
         year           = year(caldt),
         ym             = as.yearmon(caldt),
         #return and net asset value
         mtna           = as.numeric(mtna),
         mret           = as.numeric(mret)) %>% 
  filter(!is.na(mret)) %>% 
  select(-c(dateff:end_dt))
  
```

## Merge the data sets and generate data for regressions 
```{r}


df_ret_summ <- df_fund_summ %>% 
  left_join(df_fund_ret, by = c("crsp_fundno", "year")) %>% 
  filter(!is.na(mret)) %>% 
  filter(!is.na(mtna)) %>% 
  #fill in the exp_ratio based on mtna
  arrange(ym, mtna) %>% 
  mutate(exp_ratio = replace(exp_ratio, exp_ratio <= 0, NA)
         ) %>% 
#  filter(!is.na(exp_ratio)) %>% 
  group_by(ym) %>% 
  fill(exp_ratio, .direction = "downup") %>% 
  ungroup() %>% 
  mutate(mexp_ratio = exp_ratio/12) %>% 
  select(-c(fund_name, exp_ratio))
  


dff_ret_summ <- df_ret_summ %>% 
  arrange(crsp_fundno, year, ym) %>% 
  group_by(ym) %>% 
  mutate(n_mret    = mret - mexp_ratio,
         agg_mtna  = sum(mtna, na.rm = TRUE),
         weight    = mtna/agg_mtna,
         weight    = dplyr::lag(weight,1)) %>% 
  filter(!is.na(weight)) %>% 
  summarise(year      = year,
            mret_vw   = sum(weight * (mret-rf), na.rm = TRUE),
            mret_ew   = mean((mret-rf), na.rm = TRUE),
            n_mret_vw = sum(weight * (n_mret-rf),  na.rm = TRUE),
            n_mret_ew = mean((n_mret-rf), na.rm = TRUE),
            mktrf     = mktrf * 100,
            smb       = smb * 100,
            hml       = hml * 100,
            umd       = umd * 100,
            rf        = rf) %>% 
  #select(-agg_mtna) %>% 
  unique() %>% 
  mutate(mretrf_vw   = mret_vw,
         mretrf_ew   = mret_ew,
         n_mretrf_vw = n_mret_vw,
         n_mretrf_ew = n_mret_ew) %>% 
  filter(ym <= "Sep 2006")
```


## Regression results for Table 2 
```{r}
vw_reg_one <- lm(mretrf_vw ~ mktrf, data = dff_ret_summ %>% mutate(mretrf_vw = mretrf_vw * 100)
                 )
vw_reg_three <- lm(mretrf_vw ~ mktrf + smb + hml, data = dff_ret_summ %>% mutate(mretrf_vw = mretrf_vw * 100)
                   )
vw_reg_four <- lm(mretrf_vw ~ mktrf + smb + hml + umd, data = dff_ret_summ %>% mutate(mretrf_vw = mretrf_vw * 100)
                  )

net_vw_reg_one <- lm(n_mretrf_vw ~ mktrf, data = dff_ret_summ %>% mutate(n_mretrf_vw = n_mretrf_vw * 100)
                     )
net_vw_reg_three <- lm(n_mretrf_vw ~ mktrf + smb + hml, data = dff_ret_summ %>% mutate(n_mretrf_vw = n_mretrf_vw * 100)
                       )
net_vw_reg_four <- lm(n_mretrf_vw ~ mktrf + smb + hml + umd, data = dff_ret_summ %>% mutate(n_mretrf_vw = n_mretrf_vw * 100)
                      )

stargazer::stargazer(vw_reg_one, vw_reg_three, vw_reg_four, net_vw_reg_one, net_vw_reg_three, net_vw_reg_four, type = "text",report = "vct*")

```

```{r}
ew_reg_one <- lm(mretrf_ew ~ mktrf, data = dff_ret_summ %>% mutate(mretrf_ew = mretrf_ew * 100)
                 )
ew_reg_three <- lm(mretrf_ew ~ mktrf + smb + hml, data = dff_ret_summ %>% mutate(mretrf_ew = mretrf_ew * 100)
                   )
ew_reg_four <- lm(mretrf_ew ~ mktrf + smb + hml + umd, data = dff_ret_summ %>% mutate(mretrf_ew = mretrf_ew * 100)
                  )

net_ew_reg_one <- lm(n_mretrf_ew ~ mktrf, data = dff_ret_summ %>% mutate(n_mretrf_ew = n_mretrf_ew * 100)
                     )
net_ew_reg_three <- lm(n_mretrf_ew ~ mktrf + smb + hml, data = dff_ret_summ %>% mutate(n_mretrf_ew = n_mretrf_ew * 100)
                       )
net_ew_reg_four <- lm(n_mretrf_ew ~ mktrf + smb + hml + umd, data = dff_ret_summ %>% mutate(n_mretrf_ew = n_mretrf_ew * 100)
                      )

stargazer::stargazer(ew_reg_one, ew_reg_three, ew_reg_four, net_ew_reg_one, net_ew_reg_three, net_ew_reg_four, type = "text",report = "vct*")

```

# Replication of Table 3 and Figures 1 and 2

## Generate the data for bootstrap draws 

```{r}

five_mil <- df_fund_summ %>% 
  left_join(df_fund_ret, by = c("crsp_fundno", "year")) %>% 
  filter(!is.na(mret)) %>% 
  select(crsp_fundno,year,ym,mtna) %>% 
  group_by(crsp_fundno, year) %>% 
  mutate(max_tna = max(mtna, na.rm = TRUE)) %>% 
  filter(max_tna >0) %>% 
  ungroup() %>% 
  mutate(in_sample = case_when(year == 1984 & max_tna > 2.5 ~ "Y",
                               year == 1990 & max_tna > 3.2 ~ "Y",
                               year == 1995 & max_tna > 3.7 ~ "Y",
                               year == 2000 & max_tna > 4.2 ~ "Y",
                               year == 2005 & max_tna > 4.8 ~ "Y",
                               TRUE ~ "N"
                               )) %>% 
  filter(in_sample == "Y") %>% 
  select(crsp_fundno) %>% 
  unique()

funds_5mi <- five_mil$crsp_fundno


df_1 <- df_fund_summ %>% 
  left_join(df_fund_ret, by = c("crsp_fundno", "year")) %>% 
  filter(!is.na(mret)) %>% 
  filter(!is.na(mtna)) %>% 
  #fill in the exp_ratio based on mtna
  arrange(ym, mtna) %>% 
  mutate(exp_ratio = replace(exp_ratio, exp_ratio <= 0, NA)
         ) %>% 
#  filter(!is.na(exp_ratio)) %>% 
  group_by(ym) %>% 
  fill(exp_ratio, .direction = "downup") %>% 
  ungroup() %>% 
  mutate(mexp_ratio = exp_ratio/12) %>% 
  select(-c(fund_name, exp_ratio, mtna, caldt)) %>% 
  filter(crsp_fundno %in% funds_5mi) %>% 
  filter(ym <= "Sep 2006") %>% 
  group_by(crsp_fundno) %>% 
  mutate(count = n()) %>% 
  filter(count >= 60)

df_1 <- df_1 %>% 
  select(-count) %>% 
  mutate(g_ret_ex = mret - rf,
         n_ret_ex = mret - rf - mexp_ratio) %>% 
  select(-c(mret, mexp_ratio)) %>% 
  arrange(crsp_fundno, ym)

#estimation for each fund 
fit_per_fund_1n <- dlply(df_1, "crsp_fundno", function(df) lm(n_ret_ex ~ mktrf + smb + hml, data = df))
fitted_1n <- ldply(fit_per_fund_1n,tidy) %>% 
  filter(term == "(Intercept)") %>% 
  select(crsp_fundno, alp_n = estimate, t_n = statistic)


fit_per_fund_1g <- dlply(df_1, "crsp_fundno", function(df) lm(g_ret_ex ~ mktrf + smb + hml, data = df))
fitted_1g <- ldply(fit_per_fund_1g,tidy) %>% 
  filter(term == "(Intercept)") %>% 
  select(crsp_fundno, alp_g = estimate, t_g = statistic)

df_1_boot <- df_1 %>% 
  left_join(fitted_1n %>% select(alp_n, crsp_fundno), by = "crsp_fundno") %>% 
  left_join(fitted_1g %>% select(alp_g, crsp_fundno), by = "crsp_fundno") %>% 
  mutate(n_ret_ex_boot = n_ret_ex - alp_n,
         g_ret_ex_boot = g_ret_ex - alp_g)


```

## Bootstrap function 
```{r}

#ym <- unique(df_1_boot$ym)
#N_5 = length(unique(df_1_boot$crsp_fundno))

boot <- function(){

  #sample 273 months fund by fund  
  df_boot_1 <- df_1_boot %>%
    select(-year) %>% 
    group_by(crsp_fundno) %>% 
    slice_sample(n=273, replace = TRUE)
    
  #bootstrap the time index for each fund
  # ym_boot_1 <- sample(ym, 273, replace = TRUE) 
  # ym_boot_1 <- sort(ym_boot_1)
  # ym_boot_1 <- rep(ym_boot_1, N_5)
   
  # ym_boot_1_df <- data.frame(crsp_fundno = unique(df_1_boot$crsp_fundno), ym = ym_boot_1) %>% 
  #   mutate(ym = as.yearmon(ym))
   
  #obtain the bootstrapped data 
  # df_boot_1 <- ym_boot_1_df %>% 
  #   left_join(df_1_boot %>% select(-umd), by = c("crsp_fundno","ym")) %>% 
  #   na.omit()

#estimate the model using the bootstrap time-series
 fit_boot_1n <- dlply(df_boot_1, "crsp_fundno", function(df) lm(n_ret_ex_boot ~ mktrf + smb + hml , data = df))


 fitted_boot_1n <- ldply(fit_boot_1n,tidy) %>% 
    filter(term == '(Intercept)') %>% 
    select(crsp_fundno, statistic) %>% 
    rename(t_bn=statistic)
 
 
 fit_boot_1g <- dlply(df_boot_1, "crsp_fundno", function(df) lm(g_ret_ex_boot ~ mktrf + smb + hml , data = df))


 fitted_boot_1g <- ldply(fit_boot_1g,tidy) %>% 
    filter(term == '(Intercept)') %>% 
    select(crsp_fundno, statistic) %>% 
    rename(t_bg=statistic)
 
 fitted_boot_1 <- fitted_boot_1n %>% 
   left_join(fitted_boot_1g, by = "crsp_fundno")
 
}
```

## Bootstrap 100 times and collect the results 
```{r}
boot_1_out <- replicate(n=100, boot(), simplify = FALSE)  
boot_1_res <- bind_rows(boot_1_out, .id = "sample")

write.csv(boot_1_res, "./Results/boot_1_res.csv")
```

## Replication of Figure 1 and Figure 2
```{r}
boot_1_plot_ave <- boot_1_res %>% 
  select(sample,crsp_fundno,t_bn, t_bg) %>% 
  group_by(sample) %>% 
  mutate(rank_n = rank(t_bn),
         rank_g = rank(t_bg)) %>% 
  ungroup() %>% 
  group_by(rank_n) %>% 
  mutate(ave_n = mean(t_bn)) %>% 
  ungroup() %>% 
  group_by(rank_g) %>% 
  mutate(ave_g = mean(t_bg)) %>% 
  ungroup() %>% 
  select(rank_n, ave_n, rank_g, ave_g) 

boot_1_plot_ave_n <- boot_1_plot_ave %>% 
  select(rank_n, ave_n) %>% 
  unique()

boot_1_plot_ave_g <- boot_1_plot_ave %>% 
  select(rank_g, ave_g) %>% 
  unique()

plot_1 <- data.frame(actual = fitted_1n$t_n, simulated = boot_1_plot_ave_n$ave_n)

m_plot_1 <- melt(plot_1)
p1 <- ggplot(m_plot_1, aes(x = value)) + stat_ecdf(aes(colour = variable)) +
  xlim(-4,4)+
  labs(y = "", x = "")
#ecdfplot(~ actual + simulated, data=plot_1, auto.key=list(space='right'))

plot_2 <- data.frame(actual = fitted_1g$t_g, simulated = boot_1_plot_ave_g$ave_g)
#ecdfplot(~ actual + simulated, data=plot_2, auto.key=list(space='right'))

m_plot_2 = melt(plot_2)
p2 <- ggplot(m_plot_2, aes(x = value)) + stat_ecdf(aes(colour = variable)) +
  xlim(-4,4)+
  labs(y = "", x = "")

p1
p2
         
```


## Replication of Table 3 
```{r}

# net 
percent_1_n_sim <- quantile(plot_1$simulated, c(.05, .1, .2,.3,.4,.5,.6,.7,.8,.9,.95))
percent_1_n_act <- quantile(plot_1$actual, c(.05, .1, .2,.3,.4,.5,.6,.7,.8,.9,.95))

tb3_1 <- data.frame(percent_1_n_sim, percent_1_n_act)

# gross   
percent_1_g_sim <- quantile(plot_2$simulated, c(.05, .1, .2,.3,.4,.5,.6,.7,.8,.9,.95))
percent_1_g_act <- quantile(plot_2$actual, c(.05, .1, .2,.3,.4,.5,.6,.7,.8,.9,.95))

tb3_2 <- data.frame(percent_1_g_sim, percent_1_g_act)

stargazer::stargazer(tb3_1, digits= 2)  


```


# Replication of Table 4

## Bootstrap function 
```{r}

boot2 <- function(sigma){
alp_draw <- replicate(n=length(unique(df_1_boot$crsp_fundno)), rnorm(23, mean = 0, sd = sigma/sqrt(12)))

alp_draw <- data.frame(unlist(alp_draw))

alp_draw <- data.frame(unlist(alp_draw))

year <- rep(unique(df_1_boot$year), length(unique(df_1_boot$crsp_fundno)))
crsp_fundno <- rep(unique(df_1_boot$crsp_fundno), each = 23)

alp_true <- data.frame(crsp_fundno, year, alp_draw$unlist.alp_draw.) %>% rename(true_alp = alp_draw.unlist.alp_draw.)
#take df_1_boot
df_2_boot <- df_1_boot %>% 
  left_join(alp_true, by = c("crsp_fundno","year")) %>% 
  mutate(g_ret_ex_boot = g_ret_ex_boot + true_alp)

df_boot_2 <- df_2_boot %>%
  select(-year) %>% 
  group_by(crsp_fundno) %>% 
  slice_sample(n=273, replace = TRUE)

fit_boot_2 <- dlply(df_boot_2, "crsp_fundno", function(df) lm(g_ret_ex_boot ~ mktrf + smb + hml , data = df))


fitted_boot_2 <- ldply(fit_boot_2,tidy) %>% 
  filter(term == '(Intercept)') %>% 
  select(crsp_fundno, statistic) %>% 
  rename(t_b2=statistic) 
}
```

## Replicate 100 times for $\sigmas$ of 0.5, 1.0 and 1.5
```{r}
boot_2_0.5 <- replicate(n=100, boot2(sigma=0.5), simplify = FALSE)  
boot_2_0.5res <- bind_rows(boot_2_0.5, .id = "sample")

df_boot2_0.5 <- boot_2_0.5res %>% 
  group_by(sample) %>% 
  mutate(rank = rank(t_b2)) %>%
  ungroup() %>% 
  group_by(rank) %>% 
  mutate(ave_t_0.5 = mean(t_b2)) %>% 
  ungroup() %>% 
  select(ave_t_0.5) %>% 
  unique()
  

write.csv(boot_2_0.5res, "./Results/boot_2_0.5res.csv")
```

```{r}
boot_2_1 <- replicate(n=100, boot2(sigma=1), simplify = FALSE)  
boot_2_1res <- bind_rows(boot_2_1, .id = "sample")

write.csv(boot_2_1res, "./Results/boot_2_1res.csv")


df_boot2_1 <- boot_2_1res %>% 
  group_by(sample) %>% 
  mutate(rank = rank(t_b2)) %>% 
  ungroup() %>% 
  group_by(rank) %>% 
  mutate(ave_t_1 = mean(t_b2)) %>% 
  ungroup() %>% 
  select(ave_t_1) %>% 
  unique()

```

```{r}
boot_2_1.5 <- replicate(n=100, boot2(sigma = 1.5), simplify = FALSE)
boot_2_1.5res <- bind_rows(boot_2_1.5, .id = "sample")

write.csv(boot_2_1.5res, "./Results/boot_2_1.5res.csv")


df_boot2_1.5 <- boot_2_1.5res %>% 
  group_by(sample) %>% 
  mutate(rank = rank(t_b2)) %>% 
  ungroup() %>% 
  group_by(rank) %>% 
  mutate(ave_t_1.5 = mean(t_b2)) %>% 
  ungroup() %>% 
  select(ave_t_1.5) %>% 
  unique()

```

## Collect the results and generate Table 4
```{r}

tb_4 <- data.frame(quantile(plot_1$actual, c(.05, .1, .2,.3,.4,.5,.6,.7,.8,.9,.95)),
                   quantile(df_boot2_0.5$ave_t_0.5, c(.05, .1, .2,.3,.4,.5,.6,.7,.8,.9,.95)),
                   quantile(df_boot2_1$ave_t_1, c(.05, .1, .2,.3,.4,.5,.6,.7,.8,.9,.95)),
                   quantile(df_boot2_1.5$ave_t_1.5, c(.05, .1, .2,.3,.4,.5,.6,.7,.8,.9,.95))) 
  colnames(tb_4) <- c("actual", "0.5","1", "1.5")
percent_1_n_sim <- quantile(plot_1$simulated, c(.05, .1, .2,.3,.4,.5,.6,.7,.8,.9,.95))
  
percent_1_n_act <- quantile(plot_1$actual, c(.05, .1, .2,.3,.4,.5,.6,.7,.8,.9,.95))
```





